---
title: "TensorFlow 使用"
author: "Heyang Gong"
date: "`r Sys.Date()`"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup,eval=TRUE, echo=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
gongfunc::set_py()
```

This project aims to 

```
1. help me to use TensorFlow as soon as possible!
2. 系统化的学习 tensorflow 的理论和使用


```




# Part I: 快猛糙

TensorFlow is an open source software library for numerical computation **using data flow graphs**. 它是开源库，用于数值计算，用**数据流图**这个工具来实现。那么有几个问题：

- 数值计算是指什么？什么是计算？为什么说各种模型就是计算？参考计算概论课程。
- Data flow graphs 是个什么鬼？它是计算过程的一种模拟。用图这个抽象的工具来模拟了计算过程。

在Data flow graphs 这个计算框架内：

- The Keras API for TensorFlow provides a high-level interface for neural networks, with a focus on enabling fast experimentation. 专攻神经网路

- The Estimator API for TensorFlow provides high-level implementations of common model types such as regressors and classifiers. 专攻各种统计模型

- The Core TensorFlow API is a lower-level interface that provides full access to the TensorFlow computational graph. 专攻底层实现

他们都是数据流图框架内的算法，应对不同数值计算任务开发出来的计算模块。TensorFlow™ 是一个使用数据流图进行数值计算的开源软件库。图中的节点代表数学运算， 而图中的边则代表在这些节点之间传递的多维数组（张量）。


文章思考和组织过程：

```
1. Installation of TensorFlow on Ubuntu! see <github.com/rstudio/tensorflow> R中的安装如此简单愉快！ 
2. tensorflow.rstudio.com is the first article I should carefully read.
3. https://github.com/Hvass-Labs/TensorFlow-Tutorials 按照这个项目每个notebook 好好运行。
4. Practice tensorflow with traditional algorithms.

```


## Quick start 

常见问题：

1. tensorflow 是什么？解决了什么问题？ 

他是一个API， 输入一些东西，然后它输出一些东西. It aim to help us building models. --> 训练过程把循环怎么藏起来了？

2. What is its core thought of create such a API?


```{r}
library(tensorflow)
sess = tf$Session()
hello <- tf$constant("hello, TensorFlow")
sess$run(hello)
```

```{r}
file.edit("scripts/simple-things.py")
# file.edit("scripts/simple-things.ipynb") 
## 这样建立的 notebook 是无法运行的

```



## 用 R 快速使用 tensorflow

- tensorflow.rstudio.com

Tensorflow is an software library. Keras API provides a high-level interface for neural network, while estimator API is about regressors and classifiers. This website has three introduction 栏目 of Keras, Estimators and Core!


### Estimators

```{r, eval = F, echo = T}
# devtools::install_github("rstudio/tfestimators")
```

Let's have a quick start!

```{r}
## 准备数据
library(tfestimators)
indices <- sample(1:nrow(mtcars), size = 0.80 * nrow(mtcars)); str(indices)
train <- mtcars[indices, ]; str(train)
test  <- mtcars[-indices, ]

## 模型构建
# return an input_fn for a given subset of data
mtcars_input_fn <- function(data) {
  input_fn(data, 
           features = c("disp", "cyl"), 
           response = "mpg")
}
cols <- feature_columns( 
  column_numeric("disp", "cyl")
)
str(cols)
model <- linear_regressor(feature_columns = cols);str(model)

## 运行模型
model %>% train(mtcars_input_fn(train));summary(model) ## 这里似乎只训练来一轮，没有步长，也没有 epoch？ 

obs <- mtcars[1:3, ]
model %>% predict(mtcars_input_fn(obs))
```



### Keras 


- 这里用到 tensorflow 了吗？

Let's have a quick start!

数据准备和查看

```{r}
library(keras)
# mnist <- dataset_mnist()
# save(mnist,file = "~/test/data/mnist.Rdata")
load("~/test/data/mnist.Rdata")
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y

# reshape
dim(x_train) <- c(nrow(x_train), 784)
dim(x_test) <- c(nrow(x_test), 784)
# rescale
x_train <- x_train / 255
x_test <- x_test / 255

y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)
```


模型构建

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = c(784)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10, activation = 'softmax')
summary(model)

model %>% compile(
  loss = 'categorical_crossentropy',
  optimizer = optimizer_rmsprop(),
  metrics = c('accuracy')
)
summary(model)

```


模型执行和计算

```{r}

history <- model %>% fit(
  x_train, y_train, 
  epochs = 30, batch_size = 128, 
  validation_split = 0.2
)

plot(history)

model %>% evaluate(x_test, y_test)

model %>% predict_classes(x_test)
```




### core TensorFlow API

The core TensorFlow API is composed of a set of Python modules that enable constructing and executing TensorFlow graphs. The tensorflow package provides access to the complete TensorFlow API from within R.


```{r}
library(tensorflow)

## 准备数据
# Create 100 phony x, y data points, y = x * 0.1 + 0.3
x_data <- runif(100, min=0, max=1)
y_data <- x_data * 0.1 + 0.3


## 构建图模型
# Try to find values for W and b that compute y_data = W * x_data + b
# (We know that W should be 0.1 and b 0.3, but TensorFlow will
# figure that out for us.)
W <- tf$Variable(tf$random_uniform(shape(1L), -1.0, 1.0))
b <- tf$Variable(tf$zeros(shape(1L)))
y <- W * x_data + b

# Minimize the mean squared errors.
loss <- tf$reduce_mean((y - y_data) ^ 2)
optimizer <- tf$train$GradientDescentOptimizer(0.5)
train <- optimizer$minimize(loss)

## 执行和运算模型
# Launch the graph and initialize the variables.
sess = tf$Session()
sess$run(tf$global_variables_initializer())

# Fit the line (Learns best fit is W: 0.1, b: 0.3)
for (step in 1:201) {
  sess$run(train)
  if (step %% 20 == 0)
    cat(step, "-", sess$run(W), sess$run(b), "\n")
}
```

我用 python 写一个和这个类似的文件。

```{r}
getwd()
dir.create("notebooks")
# file.create("notebooks/tensorflow-r2python.ipynb")
```


## Tensorflow Tutorial Codes


https://github.com/Hvass-Labs/TensorFlow-Tutorials 是一个非常棒的库，每个模型都有 Notebooks 可以运行。

## 传统ML tensorflow practice

### Quick start

```{r, eval=F}
file.edit("scripts/linear-model.R")
gongfunc::set_py()
```

# Part II: tensorflow 系统化学习